Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-30 Response/Response 2/response-1.tex

\vspace{1eM}
\underline{\textit{Reply:}} We thank the reviewer for providing valuable and insightful comments.

\vspace{1eM}
For the resubmitted manuscript, the reviewer still has the following concerns

\begin{enumerate}
\cmnt{1} \review{Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g. III.A. More space can be left for convergence proof, which is very important. }

\resp We have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof. We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.

@@

\cmnt{2} \review{In convergence proof (48), why does the 2nd inequality hold? In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, \eqn{\leq 0} directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore feasible.  }

\resp We have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.

\cmnt{3} \review{The solutions SCA iterations \eqn{\mbf{m}^{(i)}_k} does not necessarily converge. In fact \eqn{\mbf{m}} has compact feasible region, and thus \eqn{\mbf{m}^{(i)}_k} has limit points for any specific \eqn{i}.  However \eqn{m_{*}^{(i)}} does not necessarily exist (the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent). Similar problem happens to \eqn{\mbf{w}^{(i)}_k}. }

\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} converge. The multiple solution follows from the convex objective of the original problem, which can have multiple solutions. However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32]. This approach ensures the uniqueness of the solution in each \ac{SCA} update.

Since our problem is (highly) nonconvex, there are possibly many stationary points. If we start from different initial points, we may end up in different stationary points. That is to say, the limit point of the \ac{SCA} approach is not unique. However, by regularizing the objective with a small quadratic term, the iterate in each step of the \ac{SCA} algorithm is unique. This and the fact that the set is compact ensure that the \ac{SCA} converges to a limit point. We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A. The modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).

@@

\cmnt{4} \review{Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved. Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.}

\resp As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52). Moreover, we have also mentioned that we in fact use the regularized objective in (46b) to analytically prove the convergence of the iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converges. Please refer to the paragraph before Section III-C.

@@

\cmnt{5} \review{Note that the conclusions [32, Thm 2] and [26, Thm 10] have lots of assumptions. To invoke these reference, explicit exposition should be provided to show that these conclusions can be applied to our problem. The same questions occur to the proof in Appendix B, where conclusions in [11] [36] and [37] are used. Too many details are omitted to make the proof convincing and clear. }

\resp We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-E. The convergence analysis for the primal and the \ac{ADMM} algorithms are presented in Appendix B. We have also mentioned the conditions required for showing the stationarity property of the limit point and included more mathematical steps to make the convergence proof of distributed approaches rigorous.

### 2015-07-30 Response/Response 2/response-2.tex

\begin{enumerate}

	\cmnt{1} \review{The revised paper did not address my previous comment about how to select the sub-channel ordering. I understand that finding the best sub-channel ordering requires exhaustive search which has extremely high complexity. But it is important to provide a guidance on what would be a good choice of sub-channel ordering. For example, can we achieve a good performance by using a low complexity ordering algorithm such as a greedy sub-channel ordering algorithm?}

	\resp We apologize for not clarifying the sub-channel ordering in detail in our previous manuscript. For simplicity we use random sub-channel ordering in our paper. That is, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets. As suggested by the reviewer, the greedy sub-channel ordering can also be considered while selecting the order. The greedy ordering can be based on sorting the best channel gain from each sub-channel, which is obtained by finding the highest channel norm seen between any user and the corresponding serving \ac{BS}.

	We remark that the choice of a sub-channel ordering scheme should also consider the number of backlogged packets associated with each user. We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user. We do not include in the manuscript due to space limitations, we have included in the response letter to answer the reviewers' question. We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users. The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB. The number of backlogged packets assumed for each user is provided in the corresponding captions in Figure \ref{fig-review-1}.
	\begin{figure*}[h!]
		\centering
		\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [11,8,14,6,6,2,10,10,5,6,9,5]}]{
			\includegraphics[width=0.8\textwidth]{reviewer_2_Q1B.eps}
			\label{fig-review-1a}
		}
		\hfill
		\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [8,9,12,8,12,5,4,10,8,5,7,9]}]{
			\includegraphics[width=0.8\textwidth]{reviewer_2_Q1A.eps}
			\label{fig-review-1b}
		}
		\caption{Convergence of the algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
		\label{fig-review-1}
	\end{figure*}

	Figure \ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system. As can be seen from Figure \ref{fig-review-1}\subref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets. However in Figure \ref{fig-review-1}\subref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison to the few other random ordering schemes. We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph. However, as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.

@@

	\resp
	We thank the reviewer for the insightful comment and we apologize for the lack of clarity in explaining this information in our earlier manuscript.
	\begin{enumerate}
		\item The amount of signaling overhead of the distributed algorithm and the centralized one depends on the system model of consideration. For example, let us consider a model with \eqn{N = 1} sub-channel, \eqn{K = 4} users and \eqn{N_B = 2} \acp{BS}, each serving 2 users. Let \eqn{N_T = 4} be the number of transmit antennas and \eqn{N_R = 1} be the number of receive antennas at each user. We note that a centralized algorithm requires the knowledge of all channels matrices in the system and thus the resulting amount of information exchange is proportional to the product of the numbers of users (\eqn{K}), \acp{BS} (\eqn{N_B}), and transmit and receive antennas (\textit{i.e.}, \eqn{N_T} and \eqn{N_R}).

		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a \ac{SISO} model requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase. Using this assumption, the total number of bits for channel information to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits. On the other hand, for the distributed algorithms, let us consider \eqn{6} bits for quantizing each element of the consensus vectors. Consequently, the proposed distributed solutions require \eqn{6 \times 2 \times 2} bits to be exchanged in each iteration.

		In the above example, for the same signaling overhead as in centralized method, we can perform only up to 6 \ac{SCA} updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part). This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method. However, as the number of sub-channels, users and/or the antenna elements increases, it may not be a feasible option to send complete \acp{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems. In addition to comparing the signaling overhead, we also need to consider the performance loss due to the \ac{CSI} quantization in the centralized approaches, which is beyond the scope of our paper. Generally, the performance is significantly degraded if precoders are designed with the quantized \ac{CSI} as discussed in [R1]. Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, which involves significant overhead in the backhaul usage.

		\vspace{1eM}
		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans. Signal Process}., vol 61, no. 22, pp. 5659-5674, Nov. 2013.
		\vspace{1eM}

@@

		\item Using the above discussion, we can say that when the system size is huge, it would be favorable to consider the distributed algorithm over the centralized approach due to the huge signaling overhead involved in exchanging the channels.

		\item From the above discussions, we can see that the \ac{ADMM} and primal schemes require significant overhead compared to the centralized algorithms for a small system. However, for a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective. If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Figure \ref{fig-review-2-a}. The system model considered is the same as the one used for Figure \ref{fig-review-1}\subref{fig-review-1a}.
		\begin{figure}[h!]
			\centering
			\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1C.eps}
			\caption{Convergence of the centralized and distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
			\label{fig-review-2-a}
		\end{figure}
		Note that Figure \ref{fig-review-2-a} plots the queue deviation at the \ac{SCA} update points only. The number of backlogged packets in each \ac{ADMM} iteration is not shown for clarity reason.

@@

	\end{enumerate}

	The above discussion is included in a condensed form in the first and the last paragraph of Section IV-C.

	In reality, since the channel is time-correlated, it is enough to update the precoders once per radio frame. Thus, it is not necessary for the distributed algorithm to converge until the end. Instead, the decentralized parts only need to follow the fading process when \eqn{J_{\max} > 1}. The performance of the distributed algorithm based on the dual decomposition scheme was discussed for the time-correlated fading in Section C of [12], which showed that it is enough for the distributed precoder design to follow the fading process to provide the desired performance. Studying the performance of distributed algorithms for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript. However, we take this opportunity to show a plot demonstrating this behavior for the \ac{KKT} based algorithm presented in Section IV-C of the manuscript.
	\begin{figure}[h!]
		\centering
		\includegraphics[width=0.8\columnwidth]{reviewer_2_Q2.eps}
		\caption{Expected number backlogged packets after each transmission instant for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,16,4,2 \rbrace} evaluated for \eqn{500} slots}
		\label{fig-review-2}
	\end{figure}

	Figure \ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}. The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{J_{\max} = 3,5,10}. The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange as discussed in [R2] and [R3]. The average number of backlogged packets after each transmission slot is evaluated as 
	\begin{equation}
	\chi = \sum_{k = 1}^K \; [ Q_k - \tilde{t}_k ]^+
	\end{equation}

	Unlike Algorithm 3, the centralized scheme presented in Figure \ref{fig-review-2} has no penalty term and it is used as a benchmark. In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of begin generated randomly.

	\begin{comment}
	Since we use \ac{KKT} approach, we can either use all users in the system for the precoder design or we can utilize single-cell MU-MIMO user selection presented in the literature to limit the number of users for which the precoders are designed, which leads to the faster convergence. As we can see from Figure \ref{fig-review-2}, as the arrival rate per user increases, the performance of \ac{KKT} schemes with \eqn{J_{\max} = 3,5,10} converges since the number of backlogged packets are significantly large, therefore, the same set of users will be served by the algorithm with better precoders by utilizing the memory.

	In spite of using memory and prior scheduling in the \ac{KKT} approach, isolated single \ac{BS} processing performs much better than the distributed scheme due to the limited number of iterations allowed in the algorithm. Note that the precoders are not updated for the desired users until convergence, after the limited number of iterations. However, if we perform the single cell precoder design by considering the neighboring precoders as fixed after the recent exchange as discussed in [28], we can improve the performance significantly for Algorithm 3 as shown by red curves in Figure \ref{fig-review-2}. In this approach, in between each exchange across the coordinating \acp{BS}, each \ac{BS} will perform \eqn{J_{\max} = 20} with the neighboring precoders as fixed. Once the iterations are performed to update the precoders, it is then exchanged across the coordinating \acp{BS} to perform the same procedure as mentioned earlier. 
	\end{comment}

	\vspace{1eM}
	[R2] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014

	[R3] P. Jayasinghe, A. T\"{o}lli, J. Kaleva,  M. Latva-aho, "{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015		
	\vspace{1eM}

@@

\cmnt{3} \review{If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm. For example, does there exist a fixed point of the algorithm? If so, is the fixed point of the algorithm unique? Is any fixed point of the algorithm also the optimal solution of the original problem in (20)? Assuming that the ADMM algorithm converges to a fixed point, will the interference vector in (39) converges to the actual interference in the network? These questions must be clarified in the paper. Otherwise, it is not clear how the ADMM algorithm is related to the original problem in (20). Similar questions should also be answered for the decomposition approach via KKT conditions. }

\resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithms. We want to clarify that we are able to prove the convergence of Algorithm 2 which is based on \ac{ADMM}. In our paper the number of updates for the \ac{ADMM} part is denoted by \eqn{J_{\max}}. There is a trade-off between signaling overhead and achievable performance by varying \eqn{J_{\max}}. In reality we may set \eqn{J_{\max}} to a finite value to reduce the signaling overhead. In such a case, the convergence is not guaranteed. In our simulations, the \ac{ADMM} part can find an optimal solution to the (convex) subproblem in each \ac{SCA} step when \eqn{J_{\max} = 20}.

\begin{itemize}
\item The fixed point for the algorithm exists if the distributed approaches are performed until convergence or iterated for significant number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step. In such scenarios, the iterative method in Algorithm 2 finds a fixed point such that \eqn{\mc{A}(\mbf{x}^{\ast}) = \mbf{x^{\ast}}}, \eqn{\forall \mbf{x}^{\ast} \in \mc{F}^{\ast}}, where \eqn{\mc{F}^{\ast}} is the set of all fixed points of the algorithm and \eqn{\mc{A}} denotes the Algorithm 2 at each \ac{AO} update point as in (54).

\item Note that in each \ac{SCA} step, the iterative procedure in Algorithm 2 finds a (unique) solution by solving (20) or (28) with the previous solution as the operating point. Therefore, the fixed point of Algorithm 2 depends on the initial operating point chosen for the iterative procedure. Upon convergence, the fixed point of Algorithm 2 can be distinct for different starting points chosen to initialize the iterative procedure.

\item Since the original problem is nonconvex, there exists multiple stationary point. Therefore, if the Algorithm 2 is initialized with a feasible operating point, then the limit point of the iterative algorithm is a fixed point of Algorithm 2, provided strict monotonicity of the objective and the uniqueness of the iterates are ensured in each \ac{SCA} step. Due to the fact that the limit point depends on the chosen initial operating point, there exists a set of limit points, which are also a fixed point of Algorithm 2. Therefore, all fixed points found by Algorithm 2, satisfying strict monotonicity and the uniqueness of the iterates in each \ac{SCA} step, are stationary points of the original nonconvex problem (16).

\item We also want to remark that  the proposed distributed algorithms are not based on fixed-point theory. The \ac{ADMM} part is to find a (unique) optimal solution to the strongly convex subproblem in each \ac{SCA} step. More explicitly, the \ac{ADMM} approach is used to solve the problem given in (20) based on augmented Lagrangian function which is different from fixed-point theory. However, the optimal solution of (20) is not necessarily a fixed-point of the problem.

\item When the ADMM approach converges, the interference vector is guaranteed to be equal to the actual interference seen in the network. This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables (the actual inference vectors).

\item Another point we want to make is that Algorithm 2 yields a stationary point of the original noncovex problem upon convergence and this stationary point may not be a fixed-point of the original noncovex problem, \textit{i.e.}, \eqn{f(\mbf{x}) = \mbf{x}}.

### 2015-07-30 Response/Response 2/response-3.tex

Additional Comments -

\begin{enumerate}

	\cmnts{a} - \review{The reviewer considers that closing statements regarding the applicability of the proposed schemes are missing. Since the results are quite similar (when not identical), which formulation is preferable between the centralized schemes? Which one for the distributed solutions?}

	\resp We have updated the manuscript to discuss possible options for selecting an algorithm for a specific implementation. The choice of considering a centralized approach is equally good when the number of receive antennas is larger than one, \textit{i.e.}, \eqn{N_R > 1}. However, in case of a single antenna receiver, the \ac{JSFRA} formulation outlined in Section III-B is more efficient than the \ac{MSE} reformulation, as there is no need for the receiver update, thereby reducing the complexity significantly.

@@

	As far as the distributed approaches are concerned, the primal and the \ac{ADMM} schemes are equally favorable when \eqn{N_R = 1} since the signaling required to be exchanged between the coordinating \acp{BS} involves only the scalar interference values. However, when \eqn{N_R > 1}, then the \ac{KKT} based distributed approach is more efficient than the primal and the \ac{ADMM} schemes, since it has less signaling overhead. The choice of selecting \eqn{\ell_q} norm is discussed in Section II-B last paragraph. The above information is included in Section IV last paragraph, \textit{i.e.}, before the simulations section.

	\cmnts{b} - \review{The last discussion in section IV-C could benefit from restructuring. The information on how to obtain a practical distributed precoder design and to avoid backhaul exchange is too condensed and difficult to understand.}

	\resp It has been rewritten to improve the readability as suggested by the reviewer. For additional information, the reviewer is requested to refer [R1].

	[R1] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014

@@

	\cmnts{c} - \review{For the simulation results, why not to unify configurations when possible? Having to read a different configuration for each graph is cumbersome and no additional comparisons are possible between figures. E.g. PL uniformly distributed between [0,-6] dB in Fig. 2 and [0,-3] dB in Fig. 3.}

	\resp The main purpose of considering several path loss models is simply to show that the proposed algorithms works reasonably well on various scenarios mentioned in Section V (Simulation Section). For benchmarking, we have also included the centralized algorithm to draw the difference between the other schemes. We are conducting more numerical experiments to have a more complete comparison of all the schemes. Unfortunately those results cannot be included in the current manuscript due to space limitation. We aim at making them available online as a companion technical report whey they are ready.

@@

	\cmnts{d} - \review{In Fig. 1, the description of the system model does not agree with the statement of N = 3 subchannels.}

	\resp The error has been fixed in the revised manuscript.

	\cmnts{e} - \review{In Fig. 4(b), the performance of Q-WSRME seems to be (in average) worse than that of Q-WSRM. However, that should not be the case, since Q-WSRME is taking into account the over allocation. Any reason for this?}

@@

	\cmnts{f} - \review{p 6, col 2, row 49: it should be \eqn{t_{l,k,n}} instead of \eqn{t_{l,n,k}}}

	\resp This issue is corrected in the revised manuscript.

	\cmnts{g} - \review{p 10, col 1, row 28: is it \eqn{\lambda} a dual variable?}

	\resp In fact, it should be the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}. We have fixed this problem in the revised manuscript.

### 2015-07-30 Report/convergence_centralized.tex
updated before Algorithm 2 Changes

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}. Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

@@

\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates. However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{m > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
\end{IEEEeqnarray}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds at each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured. However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.

Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update. It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}

>>>>

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem. The positive constant \me{c_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{m > 0} be the constant of strong convexity of \eqn{f} with \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} as in \cite{scutari-1}. Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}. The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}

@@

\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates. However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some constant \eqn{m > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
\end{IEEEeqnarray}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.

Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update. It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.
}
